PDBF Documentation

### 2015-05-28 Documentation.tex
Fixed typo in documentation

\section{SQL queries for PDBF elements}
PDBF uses AlaSQL as database engine. For all available features visit \url{https://github.com/agershun/alasql}. Some functionality might not yet be available because we currently use not the latest version.\\
Mostly sql syntax is standart sql, but for example attributes with spaces in their name have to be sourrounded by square brackets. E.g. SELECT attribute AS [attribute with spaces] FROM test;\\

>>>>

\section{SQL queries for PDBF elements}
PDBF uses AlaSQL as database engine. For all available features of the database visit \url{https://github.com/agershun/alasql}. Some functionality might not yet be available because we currently use not the latest version.\\[4pt]
\textbf{Note:} Mostly sql syntax is standart sql, but for example attributes with spaces in their name have to be sourrounded by square brackets. E.g. SELECT attribute AS [attribute with spaces] FROM test;\\
